Certified Symbolic Transducer with the Application of String Solver

### 2025-02-17 Paper/main.tex
add support for variable equal

Figure \ref{fig-def-FT} shows our formalization of SFTs in Isabelle / HOL. The elements $\mathcal{Q}$, $\mathcal{I}$, and $\mathcal{F}$ are intuitive when referring to Definition \ref{def-sft}. However, the transitions are not exactly the same. 
%
The set of transitions is defined by \texttt{LTTS} ( which is short for Labeled Transducer Transition System). Each transition is defined as $'q \times ('a \text{ set option }\times b) \times 'q$. There are some design decisions, which are made to make the FT formalization more flexible.

Firstly, $'a \text{ set option }$ is the type input of the transition, it accepts a set of elements of type $'a$ or \texttt{None} regarding the semantics of the type \texttt{option}. 
Accepting a set of $'a$ elements aims to express the same but more abstract semantics of the input labels in Definition \ref{def-sft}, in which an input label is a predicate. A predicate's semantics as introduced before represents a set of elements that make the predicate true. But predicates have various different forms. For instance, the interval $[1, 9]$ is a predicate that contains all elements $e$ between $1$ and $9$, i.e., $1 \leq e \leq 9$. The predicate $\lambda x : \mathbb{N}.~ x \text{ mod } 2 = 0$ denotes the set of even natural numbers. All these different forms of labels are abstracted as sets.

>>>>

Figure \ref{fig-def-FT} shows our formalization of SFTs in Isabelle / HOL. The elements $\mathcal{Q}$, $\mathcal{I}$, and $\mathcal{F}$ are intuitive when referring to Definition \ref{def-sft}. However, the transitions are not exactly the same. 
%
The set of transitions is defined by \texttt{LTTS} ( which is short for Labeled Transducer Transition System). Each transition is defined as $'q \times ('a \text{ set option }\times b) \times 'q$. There are some design decisions, which are made to make the FT formalization more abstract and flexible.

Firstly, $'a \text{ set option }$ is the input type of the transition, it accepts a set of elements of type $'a$ or \texttt{None} regarding the semantics of the type \texttt{option}. 
Accepting a set of $'a$ elements aims to express the same but more abstract semantics of the input labels in Definition \ref{def-sft}, in which an input label is a predicate. A predicate's semantics as introduced before represents a set of elements that make the predicate true. But predicates have various different forms. For instance, the interval $[1, 9]$ is a predicate that contains all elements $e$ between $1$ and $9$, i.e., $1 \leq e \leq 9$. The predicate $\lambda x : \mathbb{N}.~ x \text{ mod } 2 = 0$ denotes the set of even natural numbers. All these different forms of labels are abstracted as sets in the formalization.
